Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-21 WSSSPE3/report/WSSSPE3_review.tex
Sections 1-2: line breaks. Section 3. Recap of WSSSPE workshops.

>>>>

In his keynote address, Turk recapped the course of developments of WSSSPE
workshops alongside with his career over the past few years. The first WSSSPE
workshop was at SuperComputing in 2013, but the notion of sustainable scientific
software drew in an audience beyond supercomputing. A year later WSSSPE1.1 at
SciPy had speakers talking about how software has been sustained inside the
scientific Python community. WSSSPE2 at SuperComputing in 2014 had breakout
group discussions coming up with actionable items, and WSSSPE2.1 at SciPy 2015
was similar. Turk noted that WSSSPE3 broke free of SuperComputing this time. He
noted the different atmosphere and perspectives of the surrounding large
conferences, despite similar WSSSPE participants.
